\documentclass{SBCbookchapter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{graphicx}

\begin{document}

\section*{Machine Learning}
When most people hear \emph{Machine Learning}, they picture a robot: a dependable butler or a deadly Terminator.
But Machine Learning is not just a futuristic fantasy;
it’s already here. In fact, it has been around for decades 
in some specialized applications, such as spam filters. \\
But... what is machine learning ? \\
here we have a slightly general definition from Arthur Samuel :
\begin{quote}
Machine learning is the field of study that gives computers the ability to learn without being explicitly programmed.
\end{quote}
In other words, Machine Learning is the science or art of programming computers so they can learn from data.\\
Your spam filter is a Machine Learning
program that, given examples of spam
emails (e.g., flagged by users) and examples of regular emails,
can learn to flag spam.\\
In that case set of all emails is the \textit{training set}, and each email is called a \textit{training example}.
\section*{Types of Learning}
The first is supervised machine learning that is based on training data. it means at first giving some data to the machine and the machine training this data then it can predict answers by using these pieces of information.\\
For example assume We want a machine that can distinguish the images of dogs and cats from each other. As you can see in the picture, we first give the machine some pictures of dogs and cats and the machine trains a model by using that information then when giving the photo it can predict which one is the dog's image and which one is the cat's image. These algorithms are not able to solve complex tasks and this algorithm is probabilistic.
\\ the second is unsupervised machine learning. it uses the hidden patterns and insights from the given data. Its ability to discover similarities and differences in information makes it the ideal solution for exploratory data analysis. as you can see this is an example. in that, we want to group dogs and cats by using the difference in shapes, and the machines cluster these by using unsupervised machine learning.
the goal of this technique is to find the underlying structure of the dataset, group that data according to similarities, and represent that dataset in a compressed format.
\\ the third is semi-supervised learning that lies between supervised and unsupervised machine learning .this technique uses labeled data to ground predictions, and unlabeled data to learn the shape of the larger data distribution
\\ the last is reinforcement learning. Reinforcement Learning is a feedback-based Machine learning technique .it works like the human brain works when making some decisions by learning from experiences and improving its performance. For example, as you can see in the picture, we have a number of cells, in one of which there is a diamond, and in some of the cells there is a wall. The robot wants to follow the path to reach the diamond. it must try all the paths.
\section*{Artificial Intelligence Hierarchy}
Here we have a high level and abstract view of the AI hierarchy.\\
In the top of the hierarchy we have the \textit{Artificial Intelligence}
which includes any technique that enables machines to solve a task in a
way like humans do.\\
In a lower level, we have \textit{Machine Learning}
now we are familiar with this term, so we will not go into details.\\
In the next level, we have \textit{Artificial Neural Networks}
in simple terms, any brain-inspired machine learning model. \\
In the bottom of the hierarchy, we have \textit{Deep Learning}
In the following sections, we'll mostly focus on this level.

\section*{Representation Learning}
A machine learning model transforms its input data
into meaningful outputs, a process that is “learned” 
from exposure to known examples of inputs and outputs. 
Therefore,  the  central  problem  in  machine  learning
and  deep  learning  is  to meaningfully transform  data:
in  other  words,  to  learn  useful representations
of  the  input  data  at hand—representations that 
get us closer to the expected output. \\
Let's look at an example. \\
We have some white and black points in a cartesian plane. \\
Let's say we want to develop an algorithm that takes a coordinates
of a point and output whether it is likely to be white or black. \\
What we need here is a new representation of our data that cleanly 
separates the white points  from  the  black  points. \\
One  possible transformation is a coordinate change. \\
In this new coordinate system, the white points have the \textbf{feature}
$x < 0$ and the black points have the \textbf{feature} $x > 0$. \\
In this case we defined the coordinate change by hand: 
we used our human intelli-gence to come up with our 
own appropriate representation of the data. This 
is fine for such an extremely simple problem, 
but could you do the same if the task were to 
clas-sify images of handwritten digits?

\section*{What Is Cancer ?}
Cancer is a disease in which some of the body’s 
cells grow uncontrollably and spread to other parts of the body. \\ 
Cancer can start almost anywhere in the human body, 
which is made up of trillions of cells. Normally, 
human cells grow and multiply to form new cells as the 
body needs them. When cells grow old or become 
damaged, they die, and new cells take their place. \\
Sometimes this orderly process breaks down, and
abnormal or damaged cells grow and multiply when
they shouldn’t. These cells may form tumors, which
are lumps of tissue. Tumors can be cancerous or
not cancerous. 

\section*{Types of Cancers}
Here we have an overview of major cancer types. \\
This is not a complete introduction to cancers, 
so we will not go into details for all of them. \\
But for this context, we will focus on a special type of blood cancer
called \textit{Acute Lymphoblastic Leukemia} (ALL). \\
because in the following sections, we have a practical example
of a deep learning model that can detect ALL from blood cells.

\section*{Acute Lymphoblastic Leukemia}
Acute lymphocytic leukemia (or acute lymphoblastic leukemia, ALL)
is a type of cancer of the blood and bone marrow — 
the spongy tissue inside bones where blood cells are made. \\
The word "acute" in acute lymphocytic leukemia comes
from the fact that the disease progresses rapidly and
creates immature blood cells, rather than mature ones.
The word "lymphocytic" 
refers to the white blood cells (B-cells or T-cells) called lymphocytes, 
which ALL affects. \\
Normal lymphoblasts develop into mature, B-cells or T-cells.\\
In ALL, both the normal development of some 
lymphocytes and the control over the number of 
lymphoid cells become defective.

\section*{Cancer Detection}
But... why cancer detection is important ? \\
Diagnosing cancer at its earliest stages often provides the
best chance for a cure. \\
If you have a symptom or a screening test result that suggests cancer,
your doctor must find out whether it is due to cancer or some other
cause.
The doctor may start by asking some questions and do a physical exam. 
The doctor also may order lab tests, or other tests or procedures,
which is a long and expensive process.

\section*{Cancer Detection}
Here is where the AI comes in. \\
AI could make image interpretation—a highly subjective task—more
straightforward and reliable.
AI algorithms may pick up on patterns that are not readily
discernable to the human eye or brain.
AI can automate assessments and tasks that humans currently can
do, but take a lot of time, After the AI gives a result, a doctor simply
needs to review what the AI has done.

\section*{Practical Example}
Here we have a practical example of detecting ALL from blood cell images. \\
But before we start, let's introduce libraries \& tools we've used for this example, if you wanna
work on this field, you should use them. \\
The library we've used for this example is \textit{TensorFlow} which is a free and open-source software library for artificial intelligence. \\
TensorFlow also includes a library for deep learning called \textit{Keras} which is an open-source neural-network library written in Python. \\
The first tool is \textit{Google Colab} which is a free cloud service
that allows you to run Jupyter notebooks on Google's servers. \\
Jupyter notebook is an environment that allows you to run Python code blocks. \\
The second one is \textit{Kaggle} which is a platform for data science competitions. \\
Also it has a lot of datasets and tutorials. \\
This is not a complete machine learning course, ...

\section*{In Real Life}
Over the past several years, researchers have developed AI tools that have the potential to make cancer imaging faster, more accurate, and even more informative. And that’s generated a lot of excitement. \\
for example, AI-based computer programs have been used to help doctors interpret MRIs for more than 20 years, but research in this area is quickly evolving. \\
Although scientists are churning out AI tools for cancer imaging, the field is still nascent and many questions about the practical applications of these tools remain unanswered. \\
A recent study, for example, showed that a machine learning algorithm trained to predict cancer outcomes zeroed in on the hospital where the tumor image was taken, rather than the patient’s tumor biology.

\end{document}